Hysteresis in human computation:\\ how one task affects another

### 2015-04-27 docs/publications/2015.04_PNAS/man.tex
additional EN edits to 2015.04_PNAS man.tex; add supp_with_man.tex

	\end{tabular}
	\caption{
		The five words whose frequencies increased, and those whose 
		frequencies decreased, the most, between treatments of given 
		experiments, within labels attributed to the first test task.
		Positive values indicate that the food-exposed treatment
		used the word with higher frequency.  
		Note that the word ``food'' is always the most suppressed among
		food-exposed workers.
		Word frequencies for 
		\textit{intertask-food-objects} correspond to the labels attributed
		to image 1 (see Fig. \ref{Sfig:task1:test}) which is not necessarily 
		the first 
		test task due to the tasks being permuted.  There were five times
		as many workers in \textit{intertask-food-objects}, hence
		larger absolute differences are observed.
	}
	\label{table:top-words}
\end{table*}

@@

The probability that this guess is correct is:
\begin{align}
	\Pr\{\mathrm{correct}\vert x\} 	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
\end{align}
The probability that the optimal classifier will be correct in general,
which is by definition $\eta^*$, can be found by summing over all values of 
$x$:

\begin{align}
	\eta^* &= \sum_{x' \in \mathcal{X}} \mathrm{Pr}\{\mathrm{correct}\vert x'\}
			\mathrm{Pr}\{x'\} \\
		&= \sum_{x'\in X} \left(
				\frac{1}{2} + 
				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
			\right)
			\left(
				\frac{p_0(x') + p_1(x')}{2}
			\right)\\
		&= \frac{1 + \theta}{2}\\
		\implies \theta &= 2\eta^* - 1.
\end{align}

>>>>

	\end{tabular}
	\caption{
		The five words whose frequencies increased, and those whose 
		frequencies decreased, the most, between treatments of given 
		experiments.  The label frequencies shown apply to the first test
		task.  Positive values indicate that the food-exposed treatment
		used the word with higher frequency.  
		Note that the word ``food'' is always the most suppressed among
		food-exposed workers.  Word frequencies for 
		\textit{intertask-food-objects} correspond to the labels attributed
		to image 1 (see Fig. \ref{Sfig:task1:test}) which is not necessarily 
		the first 
		test task due to the tasks being permuted.  There were five times
		as many workers in \textit{intertask-food-objects}, hence
		larger absolute differences are observed.
	}
	\label{table:top-words}
\end{table*}

@@

The probability that this guess is correct is:
\begin{align}
	\Pr\{\mathrm{correct}\vert x\} 	&= \frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}.
\end{align}
The probability that the optimal classifier will be correct in general,
which is by definition $\eta^*$, can be found by summing over all possible
responses $x \in \mathcal{X}$:

\begin{align}
	\eta^* &= \sum_{x \in \mathcal{X}} \mathrm{Pr}\{\mathrm{correct}\vert x\}
			\mathrm{Pr}\{x\} \\
		&= \sum_{x\in X} \left(
				\frac{1}{2} + 
				\frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}
			\right)
			\left(
				\frac{p_0(x) + p_1(x)}{2}
			\right)\\
		&= \frac{1 + \theta}{2}
\end{align}

### 2015-04-27 docs/publications/2015.04_PNAS/supp_with_man.tex
additional EN edits to 2015.04_PNAS man.tex; add supp_with_man.tex

\begin{sciabstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small jobs, typically taking less than five minutes each.
A topic of ongoing research concerns designing jobs that elicit high 
quality annotations. Here we identify a feature of nearly all crowdsourcing 
jobs that acts as a strong systemic source of bias. 
Microtask jobs typically consist of a sequence 
of tasks sharing common format 
(e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask job format, we 
discover that earlier tasks have a priming effect on the worker, shifting the 
distribution of future answers by 30-50\%. 
Moreover, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
Understanding these \textit{intertask effects} is crucial 
to embracing micratask platforms in critical applications.
While intertask effects can be a source of systematic bias, 
our results suggest that, with appropriate job design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
\end{sciabstract}

>>>>

\begin{sciabstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small jobs, typically taking less than five minutes each.
A topic of ongoing research concerns designing jobs that elicit high 
quality annotations. Here we identify a feature of nearly all crowdsourcing 
jobs that acts as a strong, systemic source of bias. 
Microtask jobs typically consist of a sequence 
of tasks sharing common format 
(e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask job format, we 
discover that earlier tasks have a priming effect on the worker, shifting the 
distribution of future answers by 30-50\%. 
Moreover, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
Understanding these \textit{intertask effects} is crucial 
to embracing microtask platforms in critical applications.
While intertask effects can be a source of systematic bias, 
our results suggest that, with appropriate job design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
\end{sciabstract}
